---
title: "covid 19"
author: "Keren Gonzalez"
date: "09/29/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex?




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

`
```{r}
barchartGC(~result + Sex,data=kRdata)
```

The first bar graph shows the frequency of of COVID-19 deaths by the hundreds. In total, around 3200 people were alive and ~100 people died.  It looks like there are more people who do not die from COVID-19, but in the alive group there are more females in comparison to males. In the dead category, there are more dead males in comparison to females.

```{r}
barchartGC(~result + Sex,data=kRdata, type="percent")

```
  

This bar graph shows the percent of people who died, separated by alive and dead bar graphs. In this graph, the pink bar is males and light blue shows percent of females who died. IN the alive group around ~58% were female and 42% were male. In the dead group, ~62% were male and ~38% female. According to the graph, it looks like males are dying at a higher percentage than females in Korea.



  
## Numerical results
```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

Now we have exact percentages of the experiment. In the alive group 56% percent are female and 44% for males. In the dead group 36% were female and 64% werew male.

## Inferential results 




## Conclusions

