---
title: "covid 19"
author: "Keren Gonzalez"
date: "09/29/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex?




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

`
```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```
  

The first bar graph shows the frequency of of COVID-19 deaths by the hundreds. It looks like there are more people who do not die from COVID-19. The second bar graph shows the percent of people who died, separated by alive and dead bar graphs. In the second graph, the pink bar is males and light blue shows percent of females who died. According to the second bar graph, it looks like males are dying at higher rates than females in Korea.



  
## Numerical results


## Inferential results 




## Conclusions

